---
title: "PA1_template"
author: Weihong
date: Feb 28, 2016
output:
  md_document:
    variant: markdown_github
---

Code for reading in the dataset and/or processing the data (ignore misiing values)
Histogram of the total number of steps taken each day


```{r}
activity<-read.csv("activity.csv", header=TRUE)
activity.filter<-na.omit(activity)
steps_sum<-aggregate(activity.filter$steps, by=list(Category=activity.filter$date), FUN=sum)
hist(steps_sum$x, main="Histogram of total steps per day", xlab="Total steps")
steps_mean<-aggregate(activity.filter$steps, by=list(Category=activity.filter$date), FUN=mean)
steps_median<-aggregate(activity.filter$steps, by=list(Category=activity.filter$date), FUN=median)
```

Mean number of steps taken each day, ignoring missing values
```{r}
steps_mean
```

Median number of steps taken each day, ignoring missing values
```{r}
steps_median
```

Time series plot of the average number of steps taken
```{r}
steps_mean_interval<-aggregate(activity.filter$steps, by=list(Category=activity.filter$interval), FUN=mean)
plot(as.numeric(steps_mean_interval$Category), as.numeric(steps_mean_interval$x), type="l", xlab="intervals", ylab="mean")
```

The 5-minute interval that, on average, contains the maximum number of steps
```{r}
steps_mean_interval[which(steps_mean_interval$x==max(steps_mean_interval$x)), ]
```

Code to describe and show a strategy for imputing missing data
```{r}
a.na<-activity[!complete.cases(activity), ]
fill<-merge(a.na, steps_mean_interval, by.x="interval", by.y="Category", all.x=TRUE)
fill$steps=fill$x
fill<-fill[, c(2,3,1)]
new<-rbind(activity.filter, fill)
```

Histogram of the total number of steps taken each day after missing values are imputed
```{r}
new_sum<-aggregate(new$steps, by=list(Category=new$date), FUN=sum)
hist(new_sum$x, main="Histogram of total steps per day", xlab="Total steps")
new_mean<-aggregate(new$steps, by=list(Category=new$date), FUN=mean)
new_median<-aggregate(new$steps, by=list(Category=new$date), FUN=median)
```

mean without missing values vs. imputed missing values
```{r}
merge(steps_mean, new_mean, by="Category", all=TRUE)
```
median without missing values vs. imputed missing values
```{r}
merge(steps_median, new_median, by="Category", all=TRUE)
```

Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
All of the R code needed to reproduce the results (numbers, plots, etc.) in the report
```{r}
new$date<-as.Date(new$date)
library(chron)
new$weekend<-chron::is.weekend(new$date)
weekday<-new[which(new$weekend=='FALSE'), ]
weekend<-new[which(new$weekend=='TRUE'), ]
weekday_mean_interval<-aggregate(weekday$steps, by=list(Category=weekday$interval), FUN=mean)
weekend_mean_interval<-aggregate(weekend$steps, by=list(Category=weekend$interval), FUN=mean)
weekday_mean_interval$weekday<-"weekday"
weekend_mean_interval$weekday<-"weekend"
rbind_mean_interval<-rbind(weekday_mean_interval, weekend_mean_interval)
library(ggplot2)
qplot(Category,x,data=rbind_mean_interval, facets = weekday ~ ., geom="line", xlab="interval", ylab="mean")
```